House price

### 2023-11-24 output/paper/paper.qmd
Upload model

@@

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false

#### Workspace setup ####
library(tidyverse)
library(knitr)
library(here)
library(randomForest)

#### Read in the cleaned data ####
data <- read_csv(here("output/data/cleaned_data.csv"), 
                 show_col_types = FALSE)

#### Split training and testing sets ####
set.seed(777)
trainid <- sample(nrow(data), 0.8*nrow(data))
train <- data[trainid,]
test <- data[-trainid,]
```

```{r}
summary(data)
```
```{r}
# Install and load the required packages
library(leaflet)

# Nanjing coordinates
nanjing_coords <- c(32.0603, 118.7969)  # Latitude, Longitude

# Create a map centered around Nanjing
nanjing_map <- leaflet() %>%
  setView(lng = nanjing_coords[2], lat = nanjing_coords[1], zoom = 12) %>%
  addTiles()  # Add default map tiles

# Print the map
print(nanjing_map)

```

```{r}
data |> ggplot(aes(y=Total_Price, x=Area, color=District)) +
  geom_point() +
  geom_smooth(method = lm)
```

@@

```{r}
model_mlg <- lm(Total_Price ~., data = train)
summary(model_mlg)
predict_mlg <- predict(model_mlg, newdata = test)
mean((test$Total_Price-predict_mlg)^2)
```

```{r}
model_rf <- randomForest(Total_Price ~., data=train)
model_rf
predict_rf <- predict(model_rf, newdata = test)
mean((test$Total_Price-predict_rf)^2)

varImpPlot(model_rf)
```
